\documentclass{classes}

\setname{Kazi Afrime}{Ahamed}
\setaddress{afrimectg@gmail.com}
\setmobile{+8801632237646}
\setmail{Chattagram,Bangladesh}
\setlinkedinaccount{https://www.linkedin.com/in/afrimearaf/} 
\setgithubaccount{https://github.com/afrimearaf} 
\setthemecolor{red} 

\begin{document}
\headerview
\vspace{1ex}
%Sections
%
\setcompanyname{Company Name}
\setcontactperson{Sir}
\setclaimedposition{Post Name} 
\coverletter{ 
\indent {
I have just finished my Bachelor of Science degree in Computer Science and Engineering , have been searching for a challenging working position in the hopes of expanding myself on the job experiences and improving my skill set for further refinement.\par
I am a self-learner with a creative curiosity. I spend my days working on a variety of web development projects, ranging from backend programming to frontend design. I enjoy learning new technologies and am currently doing so.
I am a team player who enjoys meeting new people and developing deep working ties with those with whom I collaborate. I'm a very organized person who enjoys getting to the end of projects and completing things. I feel that my strong work ethics and social skills are exactly what the business need in order to ensure a pleasant work environment and effective company-client connections.\par
I appreciate your time and attention today, and I eagerly forward hearing from you. For further details, please see my entire resume/CV attached.\\
\break
Sincerely,\\
Kazi Afrime Ahamed
}

}
\end{document}